---
title: "Lab 03 - Tidy Graphics and Teamwork"
subtitle: "Due: Monday, Feb 3 at 11:59pm"
author: ""
date: ""
output:
  pdf_document: default
  html_document: default
---

*****

You may knit this document to see what the template looks like. 
**When turning a document in on Gradescope, remember to `Knit to PDF`** and 
submit that PDF document. 

Delete everything between the 5 asterisks in your final document. Also, delete
the 5 asterisks.

*****

## Packages

```{r packages, warning = FALSE, message = FALSE}
library(tidyverse)
```

## Exercise 2

```{r}
### In this chunk, implement the code for Exercise 2.
### Name your chunk and then delete this comment.

```

## Exercise 3

```{r}
### In this chunk, implement the code for Exercise 3.
### Name your chunk and then delete this comment.

```

## Exercise 4


## Exercise 5


*****

## Final checks

1. Did every team member commit?
2. Do all code chunks have names?
3. Are your figures appropriately sized?
4. Is all code and narrative following the 80 characters rule?
5. Did you proofread your narrative and run spell checker (button next to save)? 

*****



